```{r}
# Load tidyverse
library("tidyverse")
library(broom)
library (tidyr)
library(purrr)
```

```{r}
#load countrycode library
library(countrycode)
```

```{r}
data <- readRDS("/Users/giangpham/Downloads/votes.rds")

# Filter for votes that are "yes", "abstain", or "no"
votes_processed <- data %>%
  filter(data["vote"] <= 3) %>%

# Adding a year column. Since the UN has started voting in 1946, and holds one session per year, we can get the year of a UN resolution by adding 1945 to the session number.
  mutate(year=session + 1945,
         # Add a country column (convert country code to country name)
         country=countrycode(ccode, "cown", "country.name")
         )

```
"Percentage of yes votes": If a country votes yes on most resolutions, we might infer that it tends to agree with the international consensus, while if it votes no, we could assume that it tends to go against it. 

# Summarize the data:
```{r}
percent_yes <- votes_processed %>%
  summarize(total = n(),
            percent_yes=mean(vote==1)
            )
percent_yes
```
About 80% of votes that are "Yes" (the fraction of all votes in their history that were "Yes").

Summarize the data by year:
```{r}
percent_yes_by_yr <- votes_processed %>%
  group_by(year) %>%
  summarize(total = n(),
            percent_yes=mean(vote==1)
            )
percent_yes_by_yr
```

Summarize the data by country:
```{r}
percent_yes_by_country <- votes_processed %>%
  group_by(country) %>%
  summarize(total = n(),
            percent_yes=mean(vote==1)
            )
percent_yes_by_country
```
# Sorting and filtering
```{r}
#Sorting in ascending order of percent_yes
percent_yes_by_country%>%
arrange(percent_yes)
# Now sort in descending order
percent_yes_by_country%>%
arrange(desc(percent_yes))

```
The country that voted least frequently, Zanzibar, had only 2 votes in the entire dataset. Filter to remove fromm the sorted data countries that have fewer than 100 votes.

```{r}
percent_yes_by_country %>%
  arrange(percent_yes) %>%
  drop_na() %>%  # Drop any null values in the dataset
  filter(total >= 100)
```
# Visualization
```{r}
# Line plot
ggplot(percent_yes_by_yr, aes(x= year, y= percent_yes)) + geom_line()
 #Scatter plot
ggplot(percent_yes_by_yr, aes(year, percent_yes)) + geom_point()+
  geom_smooth()
```

Same Plots

```{r}
# summarize by country and by year
by_yr_country <- votes_processed %>%
  group_by(year,country) %>%
  summarize(total = n(),
            percent_yes=mean(vote==1)
            )
by_yr_country

# Filtering for multiple countries
filtered_countries <- by_yr_country %>%
  filter(country %in% c("United States", "United Kingdom",
               "France", "India")
         )
filtered_countries

# Visualizing vote trends by country (same plots)
ggplot(filtered_countries, aes(x= year, y=percent_yes,
       color=country) )+
  geom_line()
```
Separated Plots
```{r}
# Visualizing vote trends by country (separated plots)
ggplot(filtered_countries, aes(x= year, y=percent_yes,
       color=country) )+
  geom_line()+
  facet_wrap(~country)

```
# Linear Regression
(For United States)

```{r}
# Filter US
unitedStates <- by_yr_country %>%
  filter(country == "United States")

# Fitting model to US
model <- lm(percent_yes ~ year, data= unitedStates) #percent yes explained by year

summary(model)

```

The estimated slope (-0.0062393) shows how much the year affects percent_yes. 
```{r}
# Tidy version
tidy(model)

# Nesting
nested <- by_yr_country %>%
  nest(-country)

# Print the nested data for Brazil (row 7)
nested$data[[7]]
```
```{r}
# Unnest the data column to return it to its original form, so that the table again has one row for each country-year pair.
nested %>%
  unnest(data)

  by_yr_country
```

```{r}
# Fitting multiple models

# Perform a linear regression on each item in the data column (Each nested dataset) & Add another mutate that applies tidy() to each model
by_yr_country %>%
  nest(-country) %>%
  mutate(model = map(data, ~ lm(percent_yes ~ year, data = .)), 
  tidied=map(model, tidy)) #Tidy each linear regression model (Use the map() function to apply the tidy() function to each linear model in the model column, creating a new column called tidied.)


# After nesting, use the map() function within a mutate() to perform a linear regression on each dataset (i.e. each item in the data column in by_year_country) modeling percent_yes as a function of year. Save the results to the model column.


# Add one more step that unnests the tidied column
country_coefficients <- by_yr_country %>%
  nest(-country) %>%
  mutate(model = map(data, ~ lm(percent_yes ~ year, data = .)),
         tidied = map(model, tidy)) %>%
         unnest(tidied)

# Print the resulting country_coefficients variable
country_coefficients # A Model for each country.

```
```{r}
# Working with many tidy models

# Filter for the year term(slope)
slope_terms <- country_coefficients %>%
  filter(term == "year")
# Only want to get the models that were statistically significant (p-value < 0.05)
slope_terms %>%
  mutate(p.adjusted = p.adjust(p.value)) %>% # Add new column 
  filter(p.adjusted < .05)

# Filtering by adjusted p-values
filtered_countries <- country_coefficients %>%
  filter(term=="year")%>%
  mutate (p.adjusted=p.adjust(p.value))%>%
  filter(p.adjusted < .05)

# Sorting for the countries increasing most quickly
filtered_countries%>%
  arrange(desc(estimate))

# Sorting for the countries decreasing most quickly
filtered_countries%>%
  arrange(estimate)

```

# Joining and Tidying

```{r}
descriptions <- readRDS("/Users/giangpham/Downloads/descriptions.rds")

# Inner join
votes_joined <- votes_processed%>%
  inner_join(descriptions,by=c("rcid","session"))

# Filter the votes_joined dataset for votes relating to colonialism 
votes_joined %>%
  filter(co==1)  #each contains a 1 if the resolution is related to this topic and a 0 otherwise. 

# Filter, then summarize by year: US_co_by_year
US_co_by_year <- votes_joined %>%
  filter(country == "United States", co == 1) %>% # only for votes related to colonialism
  group_by(year) %>%
  summarize(percent_yes = mean(vote == 1))

# Graph the % of "yes" votes over time
ggplot(US_co_by_year, aes(year, percent_yes)) +
  geom_line()

```
```{r}
# Tidy data
votes_gathered <- votes_joined %>%
  gather(topic, has_topic, me:ec) %>%
  filter(has_topic ==1)

# Recording the topics
votes_tidied <- votes_gathered %>%
  mutate(topic = recode(topic,
                        me = "Palestinian conflict",
                        nu = "Nuclear weapons and nuclear material",
                        di = "Arms control and disarmament",
                        hr = "Human rights",
                        co = "Colonialism",
                        ec = "Economic development"))
```
```{r}
# Summarize the percentage "yes" per country-year-topic
by_country_year_topic <- votes_tidied %>%
  group_by(country, year, topic) %>%
  summarize(total = n(), percent_yes = mean(vote == 1)) %>%
  ungroup()
by_country_year_topic
```
```{r}
# Filter by_country_year_topic for just the US
US_by_country_year_topic <- by_country_year_topic %>%
  filter(country == "United States")

# Plot % yes over time for the US, faceting by topic
ggplot(US_by_country_year_topic, aes(year, percent_yes)) +
  geom_line() +
  facet_wrap(~ topic)

# Fit model on the by_country_year_topic dataset
country_topic_coefficients <- by_country_year_topic %>%
  nest(-country, -topic) %>%
  mutate(model = map(data, ~ lm(percent_yes ~ year, data = .)),
         tidied = map(model, tidy)) %>%
  unnest(tidied)

# Print country_topic_coefficients
country_topic_coefficients
```
```{r}
# Extract only cases that are statistically significant (adjusting the p-value for the number of models, and then filtering to include only significant changes)
country_topic_filtered <- country_topic_coefficients %>%
  filter(term=="year")%>%
  mutate (p.adjusted=p.adjust(p.value))%>%
  filter(p.adjusted < .05)

# Over its history, Vanuatu (an island nation in the Pacific Ocean) sharply changed its pattern of voting on the topic of Palestinian conflict. We can examine this country's voting patterns more closely.
# Create vanuatu_by_country_year_topic
vanuatu_by_country_year_topic <- by_country_year_topic %>%
  filter(country == "Vanuatu")

# Plot of percentage "yes" over time, faceted by topic
ggplot(vanuatu_by_country_year_topic, aes(year, percent_yes)) +
  geom_line() +
  facet_wrap(~ topic)
```

